---
title: "tutorials for using map of accidents"
author: "Nguyen Tuong Quang"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ac_tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r echo = FALSE}
library(Qaccidentmap)
```

## Aims of the package:
This package help you to map plot accidents rely to locations where accidents occured. Data for map are from [the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System](https://www.nhtsa.gov/Data/Fatality-Analysis-Reporting-System-(FARS)).

## Accessing the package:
```{r eval = FALSE}
library(devtools)
install_github("mrntq/Qaccidentmap")
library(Qaccidentmap)
```

## How to use:
- First, dowload data from [the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System](https://www.nhtsa.gov/Data/Fatality-Analysis-Reporting-System-(FARS)).
- Second, choose year and state number to map plot by function fars_map_state.
For example: fars_map_state(5, 2013)
